---
title: "FinalProj_2"
author: "Wafer"
date: "11/29/2019"
output: pdf_document
---


## Question 1 
### What does the player performance look like through different states in the U.S.? Are there some states tend to have better performance?

```{r}
hs_indoor18$boys_800m %>%
  filter(Rank <= 10) 

hs_indoor18$girls_800m %>%
  filter(Rank <= 10)
hs_outdoor18
```

```{r}
ggplot() + 
  geom_polygon(data=usmap, aes(x=long, y=lat, group = group),color="white", fill="grey92") +
  geom_point(data = col_outdoor18$wmen_5000m[1:200,], aes(x = lon, y = lat, shape = Level, color = Time)) +
  #scale_size(name="", range = c(2, 15)) +
  #guides(size=guide_legend("Rank")) +
  theme_void() +
  theme(legend.position = "bottom", legend.box = "vertical")


col_outdoor18$wmen_5000m <- col_outdoor18$wmen_5000m %>%
  mutate(Level = cut(col_outdoor18$men_5000m$Rank, 
                     breaks = c(-Inf, 100, 200, 300, 400, Inf), 
                     labels = c("Elite+++++", "Supreme++++", 
                                "Master+++", "Legendary++", "Distinguished+"), 
                     right = TRUE))

plot_usmap(data = windspeed, values = "Population", color = "blue") + 
   scale_fill_continuous(
     low = "white", high = "blue", name = "Population", label = scales::comma) + 
   theme(legend.position = "right")

windspeed %>%
  arrange(desc(Population))

col_outdoor18$wmen_10000m %>%
  mutate(Level = cut(col_outdoor18$wmen_10000m$Rank, 
                     breaks = c(-Inf, 100, 200, 300, 400, Inf), 
                     labels = c("Elite+++++", "Supreme++++", 
                                "Master+++", "Legendary++", "Distinguished+"), 
                     right = TRUE)) %>%
  group_by(state) %>%
  count() %>%
  arrange(desc(n)) -> tryy

tryy %>%
  left_join(windspeed, by =c("state")) %>%
  select(1, 2, 3, 6, 7, 8) -> tryy_rankbywindspeed

plot_usmap(data = windspeed, values = "Population", color = "blue") + 
   scale_fill_continuous(
     low = "white", high = "blue", name = "Population", label = scales::comma) + 
   theme(legend.position = "right")

ggplot() + 
  geom_polygon(data=usmap, aes(x=long, y=lat, group = group),color="white", fill="grey92") +
  geom_point(aes(x = tryy$lon, y = tryy$lat), size = tryy$n) +
  scale_size_continuous(c(1,10)) +
  #scale_size(name="", range = c(1, 5)) +
  #guides(colour = guide_legend(override.aes = list(size=0.3)))
  
```


```{r}
# high school 800m
plot_usmap(data = hs_outdoor18$boys_800m, values = "Rank", color = "blue") + 
  scale_fill_continuous(
    low = "white", high = "blue", name = "Ranking", label = scales::comma) + 
  theme(legend.position = "right")

# college 800m
plot_usmap(data = col_outdoor18$men_800m, values = "Rank", color = "red") + 
  scale_fill_continuous(
    low = "white", high = "red", name = "Ranking", label = scales::comma) + 
  theme(legend.position = "right")


ggplot() + 
  geom_polygon(data=usmap, aes(x=long, y=lat, group = group),color="white", fill="grey92") +
  geom_point(aes(x = col_outdoor18$men_800m$lon, y = col_outdoor18$men_800m$lat))
```


```{r}
library(cartography)
library(sf)

ggplot(tryy, aes(x = lon, y = lat)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  geom_point(aes(size = n, color = Rank)) +
  scale_size_continuous(range = c(1, 10)) 
```

# Q1 visualization - ranking
- use plot_usmap() get regional ranking with different color
- no specific pattern, distribute randomly
```{r}
plot_usmap(data = hs_outdoor18$boys_800m, values = "Rank", color = "blue", labels = TRUE) + 
  scale_fill_continuous(low = "white", high = "blue", 
                        name = "Ranking", label = scales::comma, limits = c(0, 150)) + 
  theme(legend.position = "right", 
        panel.background = element_rect(colour = "Black")) +
  labs(title = "College outdoor TF men (800m) - top 150")
  

plot_usmap(data = hs_outdoor18$girls_800m, values = "Rank", color = "red", labels = TRUE) + 
  scale_fill_continuous(low = "white", high = "red", 
                        name = "Ranking", label = scales::comma, limits = c(0, 150)) + 
  theme(legend.position = "right", 
        panel.background = element_rect(colour = "Black")) +
  labs(title = "College outdoor TF women (800m) - top 150")
```

```{r}
plot_usmap(data = col_outdoor18$men_1500m, values = "Rank", color = "blue", labels = TRUE) + 
  scale_fill_continuous(low = "white", high = "blue", 
                        name = "Ranking", label = scales::comma, limits = c(0, 150)) + 
  theme(legend.position = "right", 
        panel.background = element_rect(colour = "Black")) +
  labs(title = "College outdoor TF men (800m) - top 150") -> begin_OTF_1500_top150_m

ggsave("begin_OTF_1500_top150_wm.png", width = 20, height = 12, units = "cm")
  

plot_usmap(data = col_outdoor18$wmen_1500m, values = "Rank", color = "red", labels = TRUE) + 
  scale_fill_continuous(low = "white", high = "red", 
                        name = "Ranking", label = scales::comma, limits = c(0, 150)) + 
  theme(legend.position = "right", 
        panel.background = element_rect(colour = "Black")) +
  labs(title = "College outdoor TF women (800m) - top 150") -> begin_OTF_1500_top150_wm

ggsave("begin_OTF_1500_top150_m.png", width = 20, height = 12, units = "cm")
```
```{r}
plot_usmap(data = col_outdoor18$men_5000m, values = "Rank", color = "blue", labels = TRUE) + 
  scale_fill_continuous(low = "white", high = "blue", 
                        name = "Ranking", label = scales::comma, limits = c(0, 150)) + 
  theme(legend.position = "right", 
        panel.background = element_rect(colour = "Black")) +
  labs(title = "College outdoor TF men (800m) - top 150") 
  

plot_usmap(data = col_outdoor18$wmen_5000m, values = "Rank", color = "red", labels = TRUE) + 
  scale_fill_continuous(low = "white", high = "red", 
                        name = "Ranking", label = scales::comma, limits = c(0, 150)) + 
  theme(legend.position = "right", 
        panel.background = element_rect(colour = "Black")) +
  labs(title = "College outdoor TF women (800m) - top 150")
```





# Q1 visualization - frequency (HS)

```{r}
library(maps)                # map_data() in U.S.
usmap <- map_data("state")
```

```{r}
# function of getting subset 
sub_rndata <- function(x) {
  x %>%
    group_by(state) %>%
    count() %>%
    left_join(x, by = "state") %>%
    group_by(state) %>%
    filter(Rank == min(Rank))
}

sub_hs_otf <- map(hs_outdoor18, sub_rndata)
sub_hs_itf <- map(hs_indoor18, sub_rndata)
sub_hs_xc <- map(hs_xc18, sub_rndata)
```
- **Outdoor**
```{r}
# plotting - men 800m
# size = freq by states, rank = best ranking in that state
ggplot(sub_hs_otf$boys_800m, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_hs_otf$boys_800m,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank, alpha = 0.9)) +
  scale_color_continuous(low = "#0099FF", high = "red") + 
  scale_size_continuous(range = c(1, 12)) -> q1_m_OTF_8

ggsave("q1_m_OTF_8.png", width = 20, height = 12, units = "cm")

# plotting - wmen 800m
# size = freq by states, rank = best ranking in that state
ggplot(sub_hs_otf$girls_800m, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_hs_otf$girls_800m,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank, alpha = 0.9)) +
  scale_color_continuous(low = "#0099FF", high = "red") + 
  scale_size_continuous(range = c(1, 12)) -> q1_wm_OTF_8

ggsave("q1_wm_OTF_8.png", width = 20, height = 12, units = "cm")

# plotting - men 1600m
# size = freq by states, rank = best ranking in that state
ggplot(sub_hs_otf$boys_1600m, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_hs_otf$boys_1600m,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank, alpha = 0.9)) +
  scale_color_continuous(low = "#0099FF", high = "red") + 
  scale_size_continuous(range = c(1, 12)) -> q1_m_OTF_16

ggsave("q1_m_OTF_16.png", width = 20, height = 12, units = "cm")

# plotting - wmen 1600m
# size = freq by states, rank = best ranking in that state
ggplot(sub_hs_otf$girls_1600m, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_hs_otf$girls_1600m,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank, alpha = 0.9)) +
  scale_color_continuous(low = "#0099FF", high = "red") + 
  scale_size_continuous(range = c(1, 12)) -> q1_wm_OTF_16

ggsave("q1_wm_OTF_16.png", width = 20, height = 12, units = "cm")

# plotting - men 3200m
# size = freq by states, rank = best ranking in that state
ggplot(sub_hs_otf$boys_3200m, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_hs_otf$boys_3200m,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank, alpha = 0.9)) +
  scale_color_continuous(low = "#0099FF", high = "red") + 
  scale_size_continuous(range = c(1, 12)) -> q1_m_OTF_32

ggsave("q1_m_OTF_32.png", width = 20, height = 12, units = "cm")

# plotting - wmen 3200m
# size = freq by states, rank = best ranking in that state
ggplot(sub_hs_otf$girls_3200m, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_hs_otf$girls_3200m,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank, alpha = 0.9)) +
  scale_color_continuous(low = "#0099FF", high = "red") + 
  scale_size_continuous(range = c(1, 12)) -> q1_wm_OTF_32

ggsave("q1_wm_OTF_32.png", width = 20, height = 12, units = "cm")
```

- **indoor**
Athletes in California less likely take part in indoor game
```{r}
# plotting - men 800m
# size = freq by states, rank = best ranking in that state
ggplot(sub_hs_itf$boys_800m, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_hs_itf$boys_800m,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank, alpha = 0.9)) +
  scale_color_continuous(low = "blue", high = "red") + 
  scale_size_continuous(range = c(1, 12)) -> q1_m_ITF_8

ggsave("q1_m_ITF_8.png", width = 20, height = 12, units = "cm")

# plotting - wmen 800m
# size = freq by states, rank = best ranking in that state
ggplot(sub_hs_itf$girls_800m, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_hs_itf$girls_800m,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank, alpha = 0.9)) +
  scale_color_continuous(low = "blue", high = "red") + 
  scale_size_continuous(range = c(1, 12)) -> q1_wm_ITF_8

ggsave("q1_wm_ITF_8.png", width = 20, height = 12, units = "cm")

# plotting - men 1600m
# size = freq by states, rank = best ranking in that state
ggplot(sub_hs_itf$boys_1600m, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_hs_itf$boys_1600m,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank, alpha = 0.9)) +
  scale_color_continuous(low = "blue", high = "red") + 
  scale_size_continuous(range = c(1, 12)) -> q1_m_ITF_16

ggsave("q1_m_ITF_16.png", width = 20, height = 12, units = "cm")

# plotting - wmen 1600m
# size = freq by states, rank = best ranking in that state
ggplot(sub_hs_itf$girls_1600m, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_hs_itf$girls_1600m,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank, alpha = 0.9)) +
  scale_color_continuous(low = "blue", high = "red") + 
  scale_size_continuous(range = c(1, 12)) -> q1_wm_ITF_16

ggsave("q1_wm_ITF_16.png", width = 20, height = 12, units = "cm")

# plotting - men 3200m
# size = freq by states, rank = best ranking in that state
ggplot(sub_hs_itf$boys_3200m, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_hs_itf$boys_3200m,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank, alpha = 0.9)) +
  scale_color_continuous(low = "blue", high = "red") + 
  scale_size_continuous(range = c(1, 12)) -> q1_m_ITF_32

ggsave("q1_m_ITF_32.png", width = 20, height = 12, units = "cm")

# plotting - wmen 3200m
# size = freq by states, rank = best ranking in that state
ggplot(sub_hs_itf$girls_3200m, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_hs_itf$girls_3200m,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank, alpha = 0.9)) +
  scale_color_continuous(low = "blue", high = "red") + 
  scale_size_continuous(range = c(1, 12)) -> q1_wm_ITF_32

ggsave("q1_wm_ITF_32.png", width = 20, height = 12, units = "cm")
```


- **cross country**
```{r}
# plotting - boys 5k
# size = freq by states, rank = best ranking in that state
ggplot(sub_hs_xc$boys_XC_5k, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_hs_xc$boys_XC_5k,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank, alpha = 0.9)) +
  scale_color_continuous(low = "#009900", high = "red") + 
  scale_size_continuous(range = c(1, 12)) -> q1_XC_m_5k

ggsave("q1_XC_m_5k.png", width = 20, height = 12, units = "cm")

# plotting - girls 5k
# size = freq by states, rank = best ranking in that state
ggplot(sub_hs_xc$girls_XC_5k, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state, fontface = "italic"), data = sub_hs_xc$girls_XC_5k,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank, alpha = 0.9)) +
  scale_color_continuous(low = "#009900", high = "red") + 
  scale_size_continuous(range = c(1, 12)) -> q1_XC_wm_5k

ggsave("q1_XC_wm_5k.png", width = 20, height = 12, units = "cm") 
```

- appendix
```{r}
# boy
plot_usmap(data = hs_indoor18$boys_800m, values = "Rank", color = "red", labels = TRUE) + 
  scale_fill_continuous(low = "#0066FF", high = "#FF6600", 
                        name = "Ranking", label = scales::comma, limits = c(0, 500)) + 
  theme(legend.position = "right", 
        panel.background = element_rect(colour = "Black")) +
  labs(title = "HS indoor TF boys (800m) - top 500") -> begin_hsboy_ITF

ggsave("begin_hsboy_ITF.png", width = 20, height = 12, units = "cm")

# girl
plot_usmap(data = hs_indoor18$girls_800m, values = "Rank", color = "red", labels = TRUE) + 
  scale_fill_continuous(low = "#0066FF", high = "#FF6600", 
                        name = "Ranking", label = scales::comma, limits = c(0, 500)) + 
  theme(legend.position = "right", 
        panel.background = element_rect(colour = "Black")) +
  labs(title = "HS indoor TF girls (800m) - top 500") -> begin_hsgirl_ITF

ggsave("begin_hsgirl_ITF.png", width = 20, height = 12, units = "cm")
```

# Q3 
- As we can see the similiar statewise pattern between different events in high school indoor/outdoor track & field data. I combine the list of indoor and outdoor datasets, counting the frequency in state
```{r}
# combine the list of dataset indoor/outdoor 
bind_rows(hs_indoor18) %>%
  group_by(state) %>%
  count() %>%
  arrange(desc(n)) -> hs_in18_freq

bind_rows(hs_outdoor18) %>%
  group_by(state) %>%
  count() %>%
  arrange(desc(n)) -> hs_out18_freq

# outdoor freq
plot_usmap(data = hs_out18_freq, values = "n", color = "red", labels = TRUE) +
  scale_fill_continuous(low = "#33CCFF", high = "#FF3300", 
                        name = "freq by state", label = scales::comma) + 
  theme(legend.position = "right", 
        panel.background = element_rect(colour = "Black")) +
  ggtitle("High School outdoor Track & Field") -> q3_hs_out_freq

ggsave("q3_hs_out_freq.png", width = 20, height = 12, units = "cm")

# player distribution (indoor)
# CA, otherwise lower income
plot_usmap(data = hs_in18_freq, values = "n", color = "red", labels = TRUE) +
  scale_fill_continuous(low = "#33CCFF", high = "#FF3300", 
                        name = "freq by state", label = scales::comma) + 
  theme(legend.position = "right", 
        panel.background = element_rect(colour = "Black")) +
  ggtitle("High School intdoor Track & Field") -> q3_hs_in_freq

ggsave("q3_hs_in_freq.png", width = 20, height = 12, units = "cm")

# median income
plot_usmap(data = median_income, values = "Income", color = "red", labels = TRUE, alpha = 0.9) +
  scale_fill_continuous(low = "#FFFF00", high = "#0000FF",
                        name = "Income", label = scales::comma) + 
  theme(legend.position = "right", 
        panel.background = element_rect(colour = "Black")) +
  labs(title = "Median Household Income by State (2013-2017)") -> q3_income

ggsave("q3_income.png", width = 20, height = 12, units = "cm")
```


# Q2
- temperature
```{r}
# rank for temperature, 1 = warmer
# n frequency for hs outdoor students from states
temperature %>%
  left_join(state_position, by = "location") %>%
  left_join(hs_out18_freq, by = "state") -> temp_outfreq

# plotting
ggplot(temp_outfreq, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state, fontface = "italic"), data = temp_outfreq,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank, alpha = 0.9)) +
  scale_color_continuous(low = "#009900", high = "red") + 
  scale_size_continuous(range = c(1, 12)) +
  ggtitle("Outdoor Athletes v.s. average temperature") -> avg_temp_OTF

ggsave("avg_temp_OTF.png", width = 20, height = 12, units = "cm")
```
- rainfall
```{r}
# rank for rainfall, 1 = more rain
# n frequency for hs outdoor students from states
rainfall %>%
  left_join(state_position, by = "location") %>%
  left_join(hs_out18_freq, by = "state") -> rain_outfreq

# plotting
ggplot(rain_outfreq, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state, fontface = "italic"), data = rain_outfreq,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank, alpha = 0.9)) +
  scale_color_continuous(low = "#009900", high = "red") + 
  scale_size_continuous(range = c(1, 12)) +
  ggtitle("Outdoor Athletes v.s. average rainfall") -> rain_out

ggsave("rain_out.png", width = 20, height = 12, units = "cm")
# ---------------------------------------------------------------------
rainfall %>%
  left_join(state_position, by = "location") %>%
  left_join(hs_in18_freq, by = "state") -> rain_infreq

# plotting
ggplot(rain_infreq, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state, fontface = "italic"), data = rain_infreq,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank, alpha = 0.9)) +
  scale_color_continuous(low = "#009900", high = "red") + 
  scale_size_continuous(range = c(1, 12)) +
  ggtitle("Indoor Athletes v.s. average rainfall") -> rain
```
- humidity
```{r}
# humidity in the morning - higher = wet
# n frequency for hs outdoor students from states
humidity %>%
  left_join(state_position, by = "location") %>%
  left_join(hs_out18_freq, by = "state") %>%
  na.omit() -> humid_outfreq

# plotting
ggplot(humid_outfreq, aes(x = lon, y = lat, color = morning)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state, fontface = "italic"), data = humid_outfreq,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = morning, alpha = 0.9)) +
  scale_color_continuous(low = "#009900", high = "red") + 
  scale_size_continuous(range = c(1, 12)) +
  ggtitle("Outdoor Athletes v.s. morning humidity") -> morn_humid_OTF
  
ggsave("morn_humid_OTF.png", width = 20, height = 12, units = "cm")
# ---------------------------------------------------------------------
humidity %>%
  left_join(state_position, by = "location") %>%
  left_join(hs_in18_freq, by = "state") %>%
  na.omit() -> humid_infreq

# plotting
ggplot(humid_infreq, aes(x = lon, y = lat, color = morning)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state, fontface = "italic"), data = humid_infreq,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = morning, alpha = 0.9)) +
  scale_color_continuous(low = "#009900", high = "red") + 
  scale_size_continuous(range = c(1, 12)) +
  ggtitle("Indoor Athletes v.s. morning humidity") -> morn_humid_ITF
  
ggsave("morn_humid_ITF.png", width = 20, height = 12, units = "cm")
```
- sunshine
```{r}
# n frequency for hs outdoor students from states
sunshine %>%
  left_join(state_position, by = "location") %>%
  left_join(hs_out18_freq, by = "state") %>%
  na.omit() -> sun_outfreq

# plotting
ggplot(sun_outfreq, aes(x = lon, y = lat, color = `% Sun`)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state, fontface = "italic"), data = sun_outfreq,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = `% Sun`, alpha = 0.9)) +
  scale_color_continuous(low = "#009900", high = "red") + 
  scale_size_continuous(range = c(1, 12)) +
  ggtitle("Outdoor Athletes v.s. percentage of sun") -> sun

ggsave("sun.png", width = 20, height = 12, units = "cm")
```
- windspeed
```{r}
# rank 1 wind speed = faster
windspeed %>%
  left_join(hs_out18_freq, by = "state") -> winds_outfreq

# plotting
ggplot(winds_outfreq, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state, fontface = "italic"), data = winds_outfreq,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank, alpha = 0.9)) +
  scale_color_continuous(low = "#009900", high = "red") + 
  scale_size_continuous(range = c(1, 12)) +
  ggtitle("Outdoor Athletes v.s. wind speed") -> winds

ggsave("winds.png", width = 20, height = 12, units = "cm")
```
- elevation
```{r}
# rank for rainfall, 1 = more rain
# n frequency for hs outdoor students from states
elevation %>%
  left_join(state_position, by = "location") %>%
  left_join(hs_out18_freq, by = "state") %>%
  na.omit() -> elev_outfreq

# plotting
ggplot(elev_outfreq, aes(x = lon, y = lat, color = `Highest Elevation`)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state, fontface = "italic"), data = elev_outfreq,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = `Highest Elevation`, alpha = 0.9)) +
  scale_color_continuous(low = "#009900", high = "red") + 
  scale_size_continuous(range = c(1, 12)) +
  ggtitle("Outdoor Athletes v.s. Elevation") -> elevation_out

ggsave("elevation_out.png", width = 20, height = 12, units = "cm")
```








- population
```{r}
plot_usmap(data = windspeed, values = "Population", color = "white", 
           labels = TRUE, label_color = "grey25") + 
  scale_fill_continuous(low = "orange", high = "blue", 
                        name = "Population", label = scales::comma, 
                        limits = c(575251, 38066920)) + 
  theme(legend.position = "right", 
        panel.background = element_rect(colour = "Black")) +
  labs(title = "Statewide Population")


plot_usmap(data = windspeed, values = "Population", color = "red", 
           labels = TRUE, label_color = "grey25") + 
  scale_fill_continuous(low = "white", high = "red", 
                        name = "Population", 
                        limits = c(575251, 38066920)) +
  theme(legend.position = "right", 
        panel.background = element_rect(colour = "Black"))



left_join(usmap1, windspeed2, by = "state") -> usjoinwind
windspeed %>%
  select(`Avg. Wind Speed`, state, Population) -> windspeed2

library(mapproj)  # coord_map() projection

ggplot(data = usjoinwind, aes(x = long, y = lat, group = group, fill = Population)) +
  geom_polygon(color = "gray90", size = 0.1)  +
  coord_map(projection = "albers", lat0 = 39, lat1 = 45) +
  labs(title = "???", fill = NULL) +
  #theme_map() + 
  theme(legend.position = "right",
        panel.background = element_rect(colour = "Black")) +
  scale_fill_gradient(low = "orange", high = "blue") + # for continuous variable 
  ggrepel::geom_label_repel(aes(label = state), data = usjoinwind)




```








## keep 
- ggsave
```{r}
# single pic
ggsave("pop.png", width = 20, height = 12, units = "cm")
ggsave("otf_girls_3200m.png", width = 20, height = 12, units = "cm")

# double pics
 -> ITF_OTF_Q1
ggsave("ITF_OTF_Q1.png", width = 33.2, height = 11, units = "cm")
```

```{r}
# a plain colors filled US map
ggplot(data = usmap, mapping = aes(x = long, y = lat, group = group, fill = region)) + 
  geom_polygon(color = "gray90", size = 0.1) +
  theme(legend.position = "hide")
```
- change color
```{r}
install.packages("wesanderson")
library(wesanderson)

# Box plot
bp+scale_fill_manual(values=wes_palette(n=3, name="Darjeeling"))

# rainbow
scale_color_gradientn(colours = rainbow(5)) + 
```
- 也是漸層填滿，another solution
```{r}
library(mapproj)  # coord_map() projection

ggplot(data = usmap, aes(x = long, y = lat, group = group, fill = region)) +
  geom_polygon(color = "gray90", size = 0.1)  +
  coord_map(projection = "albers", lat0 = 39, lat1 = 45) +
  labs(title = "???", fill = NULL) +
  theme_map() + 
  theme(legend.position = "hide")
  # scale_fill_gradient(low = "orange", high = "blue")  # for continuous variable
```



## -----------------------------------------------------
# Keep (NOT USE) performance by college
- Function
```{r}
# function of getting subset 
sub_rndata <- function(x) {
  x1 <- x %>%
  group_by(state) %>%
  count()
  x <- x1 %>%
    left_join(x, by = "state") %>%
    group_by(state) %>%
    filter(Rank == min(Rank))
  return(x)
}

sub_col_otf <- map(col_outdoor18, sub_rndata)
sub_col_itf <- map(col_indoor18, sub_rndata)
```
- **outdoor**
```{r}
# plotting - wmen 800m
# size = freq by states, rank = best ranking in that state
ggplot(sub_col_otf$wmen_800m, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_col_otf$wmen_800m,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank)) +
  scale_size_continuous(range = c(1, 12)) 

# plotting - men 1500m
# size = freq by states, rank = best ranking in that state
ggplot(sub_col_otf$men_1500m, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_col_otf$men_1500m,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank)) +
  scale_size_continuous(range = c(1, 12)) 

# plotting - wmen 5000m
# size = freq by states, rank = best ranking in that state
ggplot(sub_col_otf$wmen_5000m, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_col_otf$wmen_5000m,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank)) +
  scale_size_continuous(range = c(1, 12))

# plotting - men 10000m
# size = freq by states, rank = best ranking in that state
ggplot(sub_col_otf$men_10000m, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_col_otf$men_10000m,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank)) +
  scale_size_continuous(range = c(1, 12)) 
```

- **indoor**
No California
```{r}
# plotting - men 800m
# size = freq by states, rank = best ranking in that state
ggplot(sub_col_itf$men_800m, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_col_itf$men_800m,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank)) +
  scale_size_continuous(range = c(1, 12)) 

# plotting - wmen 3000m
# size = freq by states, rank = best ranking in that state
ggplot(sub_col_itf$men_3000m, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_col_itf$wmen_3000m,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank)) +
  scale_size_continuous(range = c(1, 12)) 

# plotting - men 5000m
# size = freq by states, rank = best ranking in that state
ggplot(sub_col_itf$men_5000m, aes(x = lon, y = lat, color = Rank)) + 
  geom_polygon(data = usmap, aes(x = long, y = lat, group = group),
               color = "white", fill = "grey92") +
  # label
  ggrepel::geom_label_repel(aes(label = state), data = sub_col_itf$men_5000m,
    size = 3, label.size = 0, segment.color = "orange") + 
  # point size & ranking
  geom_point(aes(size = n, color = Rank)) +
  scale_size_continuous(range = c(1, 12)) 
```
## -----------------------------------------------------

```{r}
# mutate level
hs_indoor18$boys_800m %>%
  mutate(Level = cut(hs_indoor18$boys_800m$Rank, 
                     breaks = c(-Inf, 100, 200, 300, 400, Inf), 
                     labels = c("Elite+++++", "Supreme++++", 
                                "Master+++", "Legendary++", "Distinguished+"), 
                     right = TRUE)) -> hs_ITF_b8

# color by 5 levels - hotpot
plot_usmap(data = hs_ITF_b8, values = "Level",  labels = TRUE) + 
  theme(legend.position = "right",
               panel.background = element_rect(colour = "Black")) +
  labs(title = "A GOOD TITLE") 
  

ggplot() + 
  geom_polygon(data=usmap, aes(x=long, y=lat, group = group),color="white", fill="grey92") +
  geom_point(aes(x = hs_ITF_b8$lon, y = hs_ITF_b8$lat, color = hs_ITF_b8$Level)) +
  theme(legend.position = "bottom")

# color is the little dots
ggplot(data = hs_ITF_b8, mapping = aes(x = lon, y = lat)) + 
  geom_polygon(data=usmap, aes(x=long, y=lat, group = group),color="white", fill="grey92") +
  geom_point() +
  ggrepel::geom_label_repel(aes(label = state), data = hs_ITF_b8_best)
    
# get rank 1-10 state name
  hs_ITF_b8 %>%
    group_by(state) %>%
    summarise(min(Time)) %>%
    left_join(state_info, by = "state") %>%
    arrange(`min(Time)`) %>%
    slice(1:10) -> hs_ITF_b8_best
```





## Popular states: (WA, CA, CO, UT, TX, FL, MA, NY, NJ)

- Climate data
```{r}
## save to offline
write_csv(temperature, "./data/save/temperature.csv")
## read offline data
temp <- read_csv("./data/save/temperature.csv")
```




